Notes

### 2020-05-07 Notes/Notes.tex
setup pure binary offset run
fix Lindblad notes thanks to Chris

%opening
\title{Notes}

@@

To include the decoherence effects, we solve for master equation in Lindblad form
\begin{align}
i \hbar \partial_t \rho (t) = [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
\end{align}
where $L_j$ are the Lindblad operators for decoherence. In this study we only include lowest order approximation, i.e., the amplitude damping for non-interacting qubits. The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^\pm_j $, where $\gamma=1/T_1$ is the decoherence rate for relaxation time $T_1$. For simplicity we assume all qubits having the same relaxation time.

>>>>

%opening
%\title{Notes}

@@

To include the decoherence effects, we solve for master equation in Lindblad form
\begin{align}
  \partial_t \rho (t) = - \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
\end{align}
where $L_j$ are the Lindblad operators for decoherence. In this study we only include lowest order approximation, i.e., the amplitude damping for non-interacting qubits. The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where $\gamma=1/T_1$ is the decoherence rate for relaxation time $T_1$. For simplicity we assume all qubits having the same relaxation time.
